Investigating country-level activity and mobility patterns and their interdependencies on COVID-19 outcomes

### 2020-09-30 docs/manuscript/manuscript.tex
comments on manuscript added

\usepackage{lineno}
\renewcommand\linenumberfont{\normalfont\small}
\linenumbers

@@

@@

@@

\begin{figure}[h!]
  \centering
  \includegraphics[width=\textwidth]{c1-activity}
  \includegraphics[width=\textwidth]{c2-activity}
  \includegraphics[width=\textwidth]{c3-activity}
  \includegraphics[width=\textwidth]{c4-activity}
  \caption{Activity changes from baseline (100\%) by cluster (Google dataset).  Trends are indicated using a generalized linear (GLM) fit for each country.}
  \label{fig:act}
\end{figure}

The driving, transit and walking activities observed from navigation via Apple devices do not distinctly vary among the clusters (\autoref{fig:mob}).
This could be explained by the fact that usual activities perhaps do not require navigation.
And also since Apple Maps users are not always representative of the population, it is less likely that changes in regular activities would be discernible from these data.

\begin{figure}[h!]
  \centering
  \includegraphics[width=.9\textwidth]{c1-mobility}
  \includegraphics[width=.9\textwidth]{c2-mobility}
  \includegraphics[width=.9\textwidth]{c3-mobility}
  \includegraphics[width=.9\textwidth]{c4-mobility}
  \caption{Mobility changes from baseline (100\%) by cluster (Apple dataset). Trends are indicated using a generalized linear (GLM) fit for each country.}
  \label{fig:mob}
\end{figure}

>>>>

%\usepackage{lineno}
%\renewcommand\linenumberfont{\normalfont\small}
%\linenumbers

@@

\subsection{Significance}

@@

\subsection{Dimensionality reduction of deterministic variables}
Perhaps PCA or EFA.

@@

% \begin{figure}[h!]
%   \centering
%   \includegraphics[width=\textwidth]{c1-activity}
%   \includegraphics[width=\textwidth]{c2-activity}
%   \includegraphics[width=\textwidth]{c3-activity}
%   \includegraphics[width=\textwidth]{c4-activity}
%   \caption{Activity changes from baseline (100\%) by cluster (Google dataset).  Trends are indicated using a generalized linear (GLM) fit for each country.}
%   \label{fig:act}
% \end{figure}

% The driving, transit and walking activities observed from navigation via Apple devices do not distinctly vary among the clusters (\autoref{fig:mob}).
% This could be explained by the fact that usual activities perhaps do not require navigation.
% And also since Apple Maps users are not always representative of the population, it is less likely that changes in regular activities would be discernible from these data.

% \begin{figure}[h!]
%   \centering
%   \includegraphics[width=.9\textwidth]{c1-mobility}
%   \includegraphics[width=.9\textwidth]{c2-mobility}
%   \includegraphics[width=.9\textwidth]{c3-mobility}
%   \includegraphics[width=.9\textwidth]{c4-mobility}
%   \caption{Mobility changes from baseline (100\%) by cluster (Apple dataset). Trends are indicated using a generalized linear (GLM) fit for each country.}
%   \label{fig:mob}
% \end{figure}
